Covering Your Basis: Model Agnostic Probes of the Binary Black Hole Population

### 2022-09-25 src/tex/appendicies.tex
one last update to appendicies??? before citations of course.

\begin{eqnarray}
\tau_\lambda \sim \Gamma(a, b), \\
p(\bm{c} | \tau_\lambda) \propto \exp \big[ -\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D_r}^{\mathrm{T}} \bm{D_r} \bm{c}  \big] e^{-n\bm{c}}
\end{eqnarray}

\noindent Above $\bm{D_r}$ is the order-$r$ difference matrix, of shape $(n-r \times n)$ and $a$, $b$, shape parameters for the Gamma distribution. 
This smoothing prior removes the strong dependence on number and location of knots that arises with using splines. By adding in a very large number 
of knots such that your domain is densly populated with basis coeficients, this allows the freedom for the model to find the smoothing 
scale that the data prefers. One downside of this prior specification as noted by\ bruce{CITE BAYESIAN PSPLINES}, is a slight dependence on choice 
of the b hyper-parameter for Gamma distribution prior on $\tau_\lambda$. We reduce this affect by following the method introduced in \bruce{CITE BAYESIAN PSPLINES} 
to alleviate this. This is done by modeling $\tau_\lambda$ with a mixture model on gamma distributions with varying b hyper-parameters. 
We now replace the prior on $\tau_\lambda$ with:

\begin{align}
    \bm{p} \sim \mathcal{D}(m), \\
    p(\tau_\lambda | \bm{p}) = \sum_i^m p_i \mathcal{G}(1, b_m)
\end{align}

>>>>

\begin{eqnarray}
\tau_\lambda \propto \Gamma(a, b) \\
p(\bm{c} | \tau_\lambda) \propto \exp \big[ -\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D_r}^{\mathrm{T}} \bm{D_r} \bm{c}  \big] e^{-n\bm{c}}
\end{eqnarray}

\noindent Above $\bm{D_r}$ is the order-$r$ difference matrix, of shape $(n-r \times n)$ and $\Gamma(a,b)$ the Gamma distribution with shape parameters, $a$ and $b$. 
This smoothing prior removes the strong dependence on number and location of knots that arises with using splines. By adding in a very large number 
of knots such that your domain is densly populated with basis coeficients, this allows the freedom for the model to find the smoothing 
scale that the data prefers. One downside of this prior specification as noted by\ bruce{CITE BAYESIAN PSPLINES}, is a slight dependence on choice 
of the b hyper-parameter for Gamma distribution prior on $\tau_\lambda$. We reduce this affect by following the method introduced in \bruce{CITE BAYESIAN PSPLINES} 
to alleviate this. This is done by modeling $\tau_\lambda$ with a mixture model on gamma distributions with varying b hyper-parameters. 
We now replace the prior on $\tau_\lambda$ with:

\begin{align}
    \bm{p} \propto \mathcal{D}(m) \\
    p(\tau_\lambda | \bm{p}) = \sum_i^m p_i \Gamma(1, b_m)
\end{align}

\noindent Where above $\mathcal{D}(m)$ is a Dirichlet distribution with $m$ degrees of freedom and ones as the concentration parameters, 
and $b_m$ is an array of $m$ different b shape parameters for the Gamma distribution.
